A Note on the Period Enforcer Algorithm \\ for Self-Suspending Tasks

### 2016-06-14 LITES/LITES-Paper.tex
Comments from Reviewer B.
take out unneeded macros (compilation trouble)
add remarks on DPCP/DFLP and some minor edits
reformat for Arxiv

\input{../preamble}

@@

\papertrue 
\title{A Note on the Period Enforcer Algorithm  for Self-Suspending Tasks}

\author[1]{Jian-Jia Chen}
\author[2]{Bj\"orn B.\ Brandenburg}
\affil[1]{TU Dortmund University, Germany\\
  \texttt{jian-jia.chen@cs.uni-dortmund.de}}
\affil[2]{Max Planck Institute for Software Systems (MPI-SWS)\\
  \texttt{bbb@mpi-sws.org}}
\authorrunning{Chen and Brandenburg} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'

\Copyright{Chen and Brandenburg}%mandatory. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\subjclass{Real-time systems, Real-time schedulability, Synchronization}% mandatory: Please choose 2012 ACM classifications from http://www.acm.org/about/class/2012 . E.g., cite as "Integrated circuits". 
\keywords{period enforcer, deferred execution, self-suspension, blocking}% mandatory: Please provide 1-5 keywords
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%EditorialOffice macros (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\Volume{XXX}
\Issue{YYY}
\DateSubmission{Date of submission}
\DateAcceptance{Date of acceptance}
\DatePublished{Date of publishing}
\SectionAreaEditor{LITES section area editor}
\DOI{10.4230/LITES.xxx.yyy.p}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\pdfoutput=1 
\input{../preamble}

@@

\title{A Note on the Period Enforcer Algorithm  \\ for Self-Suspending Tasks}

\date{}

\author{Jian-Jia Chen \\ TU Dortmund University, Germany \\ \texttt{jian-jia.chen@cs.uni-dortmund.de} \and Bj\"orn B.\ Brandenburg \\ Max Planck Institute for Software Systems (MPI-SWS) \\ \texttt{bbb@mpi-sws.org}}

%\author[1]{Jian-Jia Chen}
%\author[2]{Bj\"orn B.\ Brandenburg}
%\affil[1]{TU Dortmund University, Germany\\
%  \texttt{jian-jia.chen@cs.uni-dortmund.de}}
%\affil[2]{Max Planck Institute for Software Systems (MPI-SWS)\\
%  \texttt{bbb@mpi-sws.org}}
%\authorrunning{Chen and Brandenburg} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'
%
%\Copyright{Chen and Brandenburg}%mandatory. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
%
%\subjclass{Real-time systems, Real-time schedulability, Synchronization}% mandatory: Please choose 2012 ACM classifications from http://www.acm.org/about/class/2012 . E.g., cite as "Integrated circuits". 
%\keywords{period enforcer, deferred execution, self-suspension, blocking}% mandatory: Please provide 1-5 keywords
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%EditorialOffice macros (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\Volume{XXX}
%\Issue{YYY}
%\DateSubmission{Date of submission}
%\DateAcceptance{Date of acceptance}
%\DatePublished{Date of publishing}
%\SectionAreaEditor{LITES section area editor}
%\DOI{10.4230/LITES.xxx.yyy.p}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
